paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

  #plot of distribution of propensity scores 
  # p1 <- ggplot(df, aes(x = ps, group = hasdatalabel)) + geom_density(aes(fill = hasdatalabel), alpha = 0.2) +
  # xlab('Probability of Being in the Analysis') +
  # ggtitle('Propensity Score Distribution by Group') +
  # scale_fill_discrete('') +
  # theme(legend.position = 'bottom', legend.direction = 'vertical') +
  # ylab("Density")
  # print(p1)

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_9 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]*1000-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]*1000+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Birth Rate per 1,000 People, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_9

@@

table_10 <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Birth Rate per 1,000 People, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_10
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]*1000-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]*1000+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Fertility Rate per 1,000 Women, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Fertility Rate per 1,000 Women, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

# p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]*1000-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]*1000+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = '< 0.001') %>% 
  kbl(caption = "State Data: Change in Infant Deaths per 1,000 Total Deaths, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c('< 0.001', p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Infant Deaths per 1,000 Total Deaths, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]*1000-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]*1000+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = p) %>% 
  kbl(caption = "State Data: Change in Fetal Deaths per 1,000 Total Deaths, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Fetal Deaths per 1,000 Total Deaths, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]*1000-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]*1000+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = p) %>% 
  kbl(caption = "State Data: Change in Maternal Deaths per 1,000 Total Deaths, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Maternal Deaths per 1,000 Total Deaths, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

>>>>

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_9 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Birth Rate per 1,000 People, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_9

@@

table_10 <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Birth Rate per 1,000 People, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_10
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Fertility Rate per 1,000 Women, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Fertility Rate per 1,000 Women, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

# p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = '< 0.001') %>% 
  kbl(caption = "State Data: Change in Infant Deaths per 1,000 Total Deaths, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c('< 0.001', p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Infant Deaths per 1,000 Total Deaths, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = p) %>% 
  kbl(caption = "State Data: Change in Fetal Deaths per 1,000 Total Deaths, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Fetal Deaths per 1,000 Total Deaths, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "95% CI lower" = model_no_dist$coefficients[2,1]-model_no_dist$coefficients[2,2]*1.96,
                  "95% CI upper" = model_no_dist$coefficients[2,1]+model_no_dist$coefficients[2,2]*1.96,
                  "p-value" = p) %>% 
  kbl(caption = "State Data: Change in Maternal Deaths per 1,000 Total Deaths, in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "95% CI lower" = c(model_dist$coefficients[2,1]-model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]-model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]-model_dist$coefficients[4,2]*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]+model_dist$coefficients[2,2]*1.96,
                                     model_dist$coefficients[3,1]+model_dist$coefficients[3,2]*1.96,
                                     model_dist$coefficients[4,1]+model_dist$coefficients[4,2]*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Maternal Deaths per 1,000 Total Deaths, in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```
